% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Michael John Woods (Software Engineer)}
% \address used twice to have two lines of address
\address{2132 Sterling Green Dr, Morrisville, NC 27560}
\address{Email: vtwoods@gmail.com --- Cell: (703)475-1337}

 
\begin{resume}
 
\section{Who Am I?} A \textbf{\emph{passionate}} Software Engineer working in \textbf{\emph{Virtualization}} and \textbf{\emph{Operating System}} Development with side projects and experience in \textbf{\emph{Web Development}} and \textbf{\emph{Open Source Projects}}. 
 
 
\section{EDUCATION \\ HONORS} {\sl Bachelor of Science,} Cum Laude (GPA 3.4) \\
                Virginia Polytechnic Institute and State University, Blacksburg VA. 2005-2009 \\
                Major: Computer Science Minor: Mathematics (Focus on Cryptography)\\
\\
                {\sl Masters of Science,} (GPA 3.8) \\
                Virginia Polytechnic Institute and State University, Blacksburg VA. 2009-2011 \\
                Major: Computer Science and Applications (Thesis:  CloudSpace) \\
                Graduate Research Assistant (NSF Grant 2009 - 2011)
 
\section{TECHNOLOGY} {\sl Languages:} \emph{C, Perl, Java} \\
                {\sl Operating Systems:} \emph{Linux} (Archlinux/Ubuntu), Cisco IOS, Windows
                {\sl Technologies:} Tomcat, AJAX, JSON, Java Applets, Java Bytecode Engineering, Ant, Make (Complex Build Infrastructures), GIT, SVN, Sockets, Multithreading
                {\sl Frameworks:} ZK, VMWare ESXi, Openstack
                {\sl Hobbies:} Python, Spring Security, Django, Xbox Media Center, jQuery Mobile, jQuery, OpenMPI
 
\section{PROJECTS}
\textbf{\emph{github.com/VTWoods}} \\
\textbf{Shopster} - Social Supermarket Shopping Web Application \\
\textbf{jquery-mobile fork} - Work on enhancing the jQuery Mobile events. One master pull. \\
\textbf{webinterface.mclicker} - XBMC Remote control app based on jQuery Mobile \\
\textbf{Arduino-IR-XBMC} - Perl script for accepting messages from an arduino containing remote control commands \\
\textbf{Resume} This resume and formatting files.
\textbf{\emph{gitorious.org/~vtwoods}} \\
\textbf{vtwoodss-xbmc-pandora-pithos} - Fork to enhance the plugin to use pithos \\
\textbf{\emph{http://code.google.com/u/VTWoods@gmail.com/}} \\
\textbf{annoflow} - Bytecode engineering project to annotate data and boundaries in the cloud to track and control data \\
\textbf{cloudspace} - Student Web development platform that creates virtual barriers in a single JVM to provide virtualized web servers.  Also includes framework for extending the virtual machine infrastructure into Java Applets. \\


\section{EXPERIENCE} {\sl Business Applications Programmer} \hfill Fall 1990 \\
                Allied-Signal Bendix Friction Materials Division, 
                Financial Planning Department, Latham, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed four "user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 
                {\sl Research Programmer} \hfill            Summer 1990 \\
                Psychology Department, Rensselaer Polytechnic 
                Institute 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Performed computer aided statistical analysis 
                    of data. 
                 \end{itemize} 
                {\sl Assistant Manager} \hfill        Summers 1988-89 \\
                Thunder Restaurant, Canton, CT
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 
 
\section{PUBLICATIONS} 
\begin{itemize}
\item ASEE SE Paper ``An Infrastructure for Teaching CS1 in the Cloud'' Spring 2010
\item SIGCSE Poster ``Improving Exception Messages with Exception Doctor'' Spring 2010
\item SIGCSE Workshop ``Teaching CS1 in the Cloud'' Spring 2010
\item FECS Paper ``Improving Exception Messages with Exception Doctor'' Spring 2011
\end{itemize}
\section{AWARDS}
Boy Scouts of America: Eagle Scout, Bronze Palm, and Arrow of Light
Second place (faculty and industry division) 2009 undergraduate research consortium

\end{resume}
\end{document}







